The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

The closest data we found so far is one of the six items / questions that GEM uses to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states:

In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative.

For now, we use two GEM indicators that relate to self-esteem and confidence. We look at the average "perceived capabilities" of an individual of a given country.

>>>>

The closest data we found so far is one of the six items / questions that GEM uses to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative".

For now, we use two GEM indicators that relate to self-esteem and confidence.

We look at the average "perceived capabilities" of an individual (18-64) of a given country to start a business.

We also take into account how likely the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur.
